\documentclass[a4paper,10pt]{article}

\usepackage[a4paper, total={7in, 10in}]{geometry}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage[sfdefault]{atkinson} %% Option 'sfdefault' if the base
%% font of the document is to be sans serif.
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{enumitem}

\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=cyan,
  pdftitle={Data Management Project},
}

\pagestyle{fancy}
\fancyhf{}
% \cfoot{\footnotesize Autorizzo il trattamento dei miei dati personali ai sensi del Dlgs 196 del 30 giugno 2003 e dell’art. 13 GDPR (Regolamento UE 2016/679) ai fini della ricerca e selezione del personale.}
\renewcommand{\headrulewidth}{0pt}

\title{Data Management Project \\
  \large DBMS Comparison}

\author{Leonardo Idone, 2088501}

\begin{document}

\maketitle

In this project, I will attempt to qualitatively compare two different
data models and their associated technologies. Specifically, the
comparison will include the Resource Description Framework and the
Relational Model. It will be conducted in the following manner:

\begin{enumerate}
  \item Choosing a dataset and an associated real-world scenario
  related to its use.
  \item Creating two implementations of the dataset, based on the
  requirements outlined in the previous steps.
  \item Importing the respective implementations and the dataset into
  a relational database and a triplestore.
  \item Comparing various aspects of the two solutions, both practical
  and conceptual (e.g. query language, memory usage, query execution
  speed, model flexibility in representing the dataset.).
\end{enumerate}
For this purpose, the chosen dataset, RDBMS and triplestore are:

\begin{itemize}
  \item Dataset(s): \href{https://datasets.imdbws.com/}{The IMDb
    Non-Commercial Datasets}, for their size, ease of access and
  simple approachability, which contains the full IMDb website with
  all its information regarding movies, actors, and their relations.
  \item RDBMS: \href{https://www.postgresql.org/}{PostgreSQL}, being
  open-source, mature and on-par with current industry standards.
  \item RDF Store (triplestore):
  \href{https://jena.apache.org/documentation/fuseki2/}{Apache Jena
    Fuseki}, for the same reasons as Postgres.
\end{itemize}

\end{document}


%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
